Data Preparation

### 2019-01-10 Data Preparation.Rmd

#### AoD from ILOs
In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs and then we take the unique combination of course and AoD in case a course had several ILOs covering the same AoD.
```{r}
d_AoD_ILO <- d_ILO %>%
  select(Code, AoD) %>%
  unique

@@

#### AoD from Assessment Type
In order to determine which AoD each course covers with its assessments, we need to create a binary matrix which indicates which AoD(s) each assessment type covers. We have created such matrix on our google drive and we save it in the following piece of code as `map_assessment_AoD`. `map_assessment_AoD` indicates that, for instance, the assessment type `Essay` covers the AoD `Critical Thinking Skills`, `Communication Skills` and `Writing Skill`.
```{r}
map_assessment_AoD <- as.matrix(gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216')[,lists$AoD] %>%
                                  mutate_all(as.logical))
rownames(map_assessment_AoD) <- lists$Assessment
print(map_assessment_AoD[1:5, 8:12])
```

Now that we have the matrix `map_assessment_AoD`, we create the tibble `d_assessment_clean` which only contains the assessments that are covered by each course and we loop through its rows to determine which AoD, each assessment covers. In the loop, we first extract the row of `d_assessment_clean` and save it as `observation` and determine the corresponding assessment which we save as `assessment`. Then we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
```{r}
d_AoD_assessment <- tibble(Code        = character(0),
                           Assessment  = character(0),
                           AoD         = character(0))

@@

print(d_AoD_assessment)
```

Similarly to what we did with the tibble `d_AoD_ILO`, we first eliminate the AoD that are not covered by the assessments and then we take the unique combination of course and AoD in case a course had several assessments covering the same AoD.
```{r}
d_AoD_assessment <- d_AoD_assessment %>%
  select(Code, AoD) %>%
  unique
print(d_AoD_assessment)
```

#### Combining AoD from ILOs and from assessments
Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `unique` in case a course covers an AoD with both its ILOS and its assessments.
```{r}
d_AoD <- rbind(d_AoD_ILO, d_AoD_assessment) %>%
  unique %>%
  arrange(Code)
print(d_AoD)
```

>>>>

#### AoD from ILOs
In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs and then we take the unique combination of course and AoD in case a course had several ILOs covering the same AoD.
```{r d_AoD_ILO}
d_AoD_ILO <- d_ILO %>%
  select(Code, AoD) %>%
  unique

@@

#### AoD from Assessment

In order to determine which AoD each course covers with its assessments, we need to create a binary matrix which indicates which AoD(s) each assessment type covers. We have created such matrix on our google drive and we save it in the following piece of code as `map_assessment_AoD`. `map_assessment_AoD` indicates that, for instance, the assessment type `Essay` covers the AoD `Critical Thinking Skills`, `Communication Skills` and `Writing Skill`.
```{r map_assessment_AoD}
map_assessment_AoD <- as.matrix(gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216')[,lists$AoD] %>%
                                  mutate_all(as.logical))
rownames(map_assessment_AoD) <- lists$Assessment
print(map_assessment_AoD[1:5, 8:12])
```

Now that we have the matrix `map_assessment_AoD`, we create the tibble `d_assessment_clean` which only contains the assessments that are covered by each course and we loop through its rows to determine which AoD, each assessment covers. In the loop, we first extract the row of `d_assessment_clean` and save it as `observation` and determine the corresponding assessment which we save as `assessment`. Then we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
```{r d_AoD_assessment}
d_AoD_assessment <- tibble(Code        = character(0),
                           Assessment  = character(0),
                           AoD         = character(0))

@@

rm(map_assessment_AoD, observation, AoD, AoD_covered, assessments, i)
```

Similarly to what we did with the tibble `d_AoD_ILO`, we first eliminate the AoD that are not covered by the assessments and then we take the unique combination of course and AoD in case a course had several assessments covering the same AoD.
```{r d_AoD_assessment distinct}
d_AoD_assessment <- d_AoD_assessment %>%
  select(Code, AoD) %>%
  distinct
print(d_AoD_assessment)
```

#### Combining AoD from ILOs and from assessments
Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `unique` in case a course covers an AoD with both its ILOS and its assessments.
```{r rbind d_AoD_ILO and d_AoD_assessment}
d_AoD <- rbind(d_AoD_ILO,
               d_AoD_assessment) %>%
  distinct %>%
  arrange(Code)

rm(d_AoD_ILO, d_AoD_assessment)
print(d_AoD)
```
